


https://www.youtube.com/watch?v=D-bd3CcNBA0
https://www.sciencedirect.com/science/article/pii/S1125786515000247
https://rstudio-pubs-static.s3.amazonaws.com/160964_2a564fa749db462ab02eb899909ec500.html


```{r}
#install.packages("measuRing")
library(measuRing)
```


Example using supplied file


```{r}
image1 <- system.file("P105_a.tif", package = "measuRing")
image1
```

All in one go
```{r}
detect1 <- ringDetect(image1)
detect1$'ringWidths'

```


Step by step
```{r}
par(mfrow=c(2,1))
gray <- imageTogray(image1)
xrange <- range(0:ncol(gray)) + c(-1,1)
yrange <- range(0:nrow(gray)) + c(-1,1)    
plot(xrange,yrange,xlim=xrange,ylim=yrange,xlab='',
      ylab='',type='n',asp=0)
  rasterImage(gray,xrange[1],yrange[1],xrange[2],yrange[2])    

smoothed <- graySmoothed(image1,ppi=1000)
Smooth <- ts(smoothed)
main. <- 'Smoothed gray'
plot(Smooth,xlab = 'Column', main=main.,
     ylab = 'Smoothed gray',col = 'gray')

```

Now try with our own image:

```{r}

image2 <- "images/DSC_1388-crop.tif"

par(mfrow=c(3,1))

gray <- imageTogray(image2)
xrange <- range(0:ncol(gray)) + c(-1,1)
yrange <- range(0:nrow(gray)) + c(-1,1)    
plot(xrange,yrange,xlim=xrange,ylim=yrange,xlab='',
     ylab='',type='n',asp=0)
rasterImage(gray,xrange[1],yrange[1],xrange[2],yrange[2])    

av_gray <- apply(gray, 2, mean)
av_gray_mean_rolling_mean <- zoo::rollmean(av_gray,100, align = "center")
plot(av_gray, type='l',asp=0, col='gray')
lines(av_gray_mean_rolling_mean, col="red")

# Showing that the automated detction in the package is not working so well
smoothed <- graySmoothed(image2, rgb = c(0.3, 0.6, 0.1))
plot( ts(smoothed),xlab = 'Column',col = 'gray')

```








---------------
gray <- imageTogray(image2)
xrange <- range(0:ncol(gray)) + c(-1,1)
yrange <- range(0:nrow(gray)) + c(-1,1)    
plot(xrange,yrange,xlim=xrange,ylim=yrange,xlab='',
     ylab='',type='n',asp=0)
rasterImage(gray,xrange[1],yrange[1],xrange[2],yrange[2])    


gray2 <- imageTogray(image2, p.row = 0.1)
xrange <- range(0:ncol(gray)) + c(-1,1)
yrange <- range(0:nrow(gray)) + c(-1,1)    
plot(xrange,yrange,xlim=xrange,ylim=yrange,xlab='',
     ylab='',type='n',asp=0)
rasterImage(gray,xrange[1],yrange[1],xrange[2],yrange[2])    

image2 <- "~/Downloads/dan_tree/DSC_1388-crop_BW.tif"


measuRing